Biologically-Constrained 3D Agglomeration for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
paper: major updates

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
	\caption{Biological constraints for 3D segments in Connectomics.}
	\label{fig:bc}
\end{figure}

The field of connectomics is concerned about reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
%These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
For the agglomeration, most methods do not make use of the biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if it is the case for larger volumes.

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We here present a new agglomeration method that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser}b). 
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser}c).

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions. 
With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions.
\TODO{refer to figure 1}
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions.
First, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
Then, a region-based CNN classifier to detect errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
Last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

>>>>

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
	\caption{Biological constraints for 3D segments in Connectomics.}
	\label{fig:biological_constraints}
\end{figure}

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For the agglomeration, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if that is the case for larger volumes.

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We present a new agglomeration framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b). 
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions. 
With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:biological_constraints}).
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-14 papers/eccv2018/2_method.tex
paper: major updates

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
	\label{fig:teaser_pipeline}
\end{figure}
% \begin{figure*}[t!]
% 	\begin{center}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
%In a split error, two segments should have been merged into one neuronal process. 
%In a merge error, one segment corresponds to more than one neuron.
%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
%Our goal is to identify locations of split errors and merge the corresponding segments automatically.

\TODO{[refer to teaser figure of the pipeline]}
\TODO{[need to be concise here]}
\TODO{[we use biological constraints]}
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation.
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation.
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints.
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmenation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

@@

%A typical approach for generating edges produces one between all adjacent segments. 
%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
%However, this method produces too many edges in the graph for graph-based optimization approaches. 
Our key observation is that if two segments belong to the same neural structure, their skeleton end points should satisfy certain geomtry constraints.
%We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

\TODO{maybe good to have equation, to make the biological constraints stand out more}
Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold. \TODO{what's the intuition}
First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Learning-based Edge Weight}
\label{sec:edge-weights}
We aim to assign edge weights $w_e$ to each edge corresponding to the possibility of two nodes belonging to the same neural structure.
W, we train a 3D CNN model to learn these geometric contraints for valid connection between two segments from labeled volume.

\noindent\textbf{Edge Probability}
As it's hard to manually design the weight
Below, we describe the network we trained to predict $p_e$.

%\subsubsection{Network Architecture}
Our network is a feedforward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size \TODO{xx}.

@@

\noindent\textbf{Edge Weight}
To add more control.. \TODO{what's the intuition}
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}
\end{align}
, where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
%The output of this final pooling step is flattened into a 1D vector that is input into . 
%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
%All of the other activation functions are .

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}
intro: blah,blah. \TODO{can we have a formula here?}

%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized ``lifted'' multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called ``lifted'' edges. 
Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron given all such possible paths in the graph between the nodes.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser-image.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
	\label{fig:teaser_pipeline}
\end{figure}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
In a split error, two segments should have been merged into one neuronal process (Fig.~\ref{fig:improved-reconstruction}). 
In a merge error, one segment corresponds to more than one neuron.
Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.

Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

@@

%A typical approach for generating edges produces one between all adjacent segments. 
%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
%However, this method produces too many edges in the graph for graph-based optimization approaches. 
Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $30\times$, with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately 70\% of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.
These parameters follow empirically from noise in the skeleton generation process. 
There are occasionally spurious branches and other artifacts and these thresholds mitigate the influence of these degenerate locations.
We provide a fuller analysis in the supplemental materials.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Learning-based Edge Weight}
\label{sec:edge-weights}
We assign an edge weight $w_e$ to each edge corresponding to the probability that two nodes belong to the same neuronal process.
We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.

\noindent\textbf{Edge Probability}
To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size $2\times2\times1$ in the first two blocks and $2\times2\times2$ in the third.

@@

\noindent\textbf{Edge Weight}

Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}
\end{align}
, where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
This particular weighting scheme allows us to optimize for a Bayesian network defined on the graph~\cite{keuper2015efficient,andres2011probabilistic}.

%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
%The output of this final pooling step is flattened into a 1D vector that is input into . 
%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
%All of the other activation functions are .

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}

After graph construction, we segment the graph into a globally consistent manner while enforcing topological constraints on the output.

%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized ``lifted'' multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called ``lifted'' edges. 
Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
paper: major updates

Our proposed method is designed for very large connectomics datasets. 
Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
The following three datasets contain from 4 to 40 times more volume than the CREMI datasets.

@@

%\subsubsection{Fib-25}
\noindent\textbf{Fib-25}
The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}. This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$. 
There is currently a reconstruction challenge based on this sample.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.

@@

\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates.

@@

\noindent\textbf{Graph Partition} \TODO{parameters?}

@@

We use both precision and recall to evaluate the convolutional neural network and multicut outputs. 
Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.

>>>>

Our proposed method is designed for very large connectomics datasets. 
Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
The following datasets contain 4 times more volume than the CREMI datasets.

@@

%\subsubsection{Fib-25}
%\noindent\textbf{Fib-25}
%The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}. This sample is %imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ %voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$. 
%There is currently a reconstruction challenge based on this sample.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.

@@

\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

@@

\noindent\textbf{Graph Partition}
We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
For our multicut analysis we consider $\beta = 0.5$.

@@

We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.
